---
title: "Capitals of the World and their Population"
author: "H. Richter"
always_allow_html: yes
date: "27. Oktober 2016"
output: html_document
---

In the following map the capitals of the world are marked
  
- For each capital the name of the city, the country it belongs to and its population is given in the popup
- The popups are clustered: Please zoom in
- The circle size represent the population of the capital
  
The data were taken from [Laenderdaten](https://www.laenderdaten.info/download/capitals.csv). The mapping data are from [Open Street Map](http://www.openstreetmap.org/).
  

```{r, comment="", echo=FALSE}
## Downloading the data:

# download data
download.file("https://www.laenderdaten.info/download/capitals.csv", 
              destfile="./Capitals.csv") 

# read data
Capitals <- read.csv("./Capitals.csv", sep = ";")
```

```{r, warning=FALSE, message = FALSE, fig.width = 9, echo=FALSE}
library(leaflet)

Capitals %>% 
      leaflet() %>%
      addTiles() %>%
      addMarkers(popup = paste(Capitals$City..en.,
                               " (", Capitals$Country..en., "), ",
                               "Population: ", 
                               Capitals$Population,
                               sep = ""),
                 clusterOptions = markerClusterOptions()) %>%
      addCircles(weight = 1, radius = sqrt(Capitals$Population) * 100)

```

## Code Chunks
  
The following code chunks were used:
  
```{r, comment="", eval=FALSE}

# download data
download.file("https://www.laenderdaten.info/download/capitals.csv", 
              destfile="./Capitals.csv") 

# read data
Capitals <- read.csv("./Capitals.csv", sep = ";")
```

```{r}
# labels
print(names(Capitals))
```
  
```{r, warning=FALSE, fig.width = 9, eval=FALSE}
library(leaflet)

Capitals %>% 
      leaflet() %>%
      addTiles() %>%
      addMarkers(popup = paste(Capitals$City..en.,
                               " (", Capitals$Country..en., "), ",
                               "Population: ", 
                               Capitals$Population,
                               sep = ""),
                 clusterOptions = markerClusterOptions()) %>%
      addCircles(weight = 1, radius = sqrt(Capitals$Population) * 100)

```